Cluster Difference Imaging Photometric Survey (CDIPS) II: A Jupiter-Sized Planet in IC~2602

### 2020-05-08 paper/ms.tex
update paper

@@

\tn\ (TIC 460205581, GAIA DR2 5251470948229949568) was observed by the
TESS spacecraft from X to Y in two-minute cadence mode.

@@

@@

\subsubsection{Kinematics}

Gaia

do a 5 subplot olympic arrangement...

plx vs pmdec
plx vs pmra
pmdec vs pmra
plx vs rv
ra vs dec

(or could just do 2 3d plots... one of positions, one of velocities. i
like this idea best, tbh.).

...
OR could do it as a corner plot, 6 dimensions...

ra
dec
plx
pmra
pmdec
rv

this would be sicker.

@@

\tn\ is in its expected position relative to the other members along
the cluster isochrone.  This photometrically limits the presence of
binary companions in \tn\ system, to a magnitude difference of perhaps
half the brightness of the target star.

Figure~\ref{fig:hr} also shows that the membership census of \cn\ is
likely incomplete.  We defined the reference ``neighborhood'' as the
group of at most $10^4$ randomly selected non-member stars within 5
standard deviations of the mean \cn\ 1 right ascension, declination,
and parallax.  We queried Gaia DR2 for these stars using
\texttt{astroquery} \citep{astroquery_2018}.  Many low-mass stars
appear above the main sequence, even though they were not identified
as 5-dimensional kinematic members through the unsupervised
\citet{cantat-gaudin_gaia_2018} membership assignment process.

@@

>>>>

TESS \citep{ricker_transiting_2015}.

@@

\tn\ (GAIA DR2 5251470948229949568) was observed by the
TESS spacecraft from X to Y in two-minute cadence mode.
The star was designated
TIC\,460205581 in the TESS Input Catalog
\citep{stassun_TIC_2018,stassun_TIC8_2019}.
%FIXME make words more original
The pixel data for an
$11\times11$ array surrounding \tn\ were averaged into 2-minute
stacks by the onboard computer.  Each 2048$\times$2048 image from the
CCD was also averaged into 30-minute stacks, and saved as a ``full
frame image'' (FFI).

%FIXME make words more original
The pixel data for an
The 2-minute stacks for \tn\ were reduced to lightcurves by the
Science Processing Operations Center (SPOC) at NASA
Ames~\citep{jenkins_tess_2016}.  We mainly used the Presearch Data
Conditioning (PDC) lightcurve.  The PDC lightcurve aperture used
pixels chosen to maximize the SNR of the total flux of the target
\citep{smith_finding_2016}.  Non-astrophysical variability
was removed by fitting out trends common to many stars
\citep{smith_kepler_2012,stumpe_multiscale_2014}.

%FIXME make words more original
As an independent check on the 2-minute SPOC lightcurve, we examined
the lightcurve based upon 30-minute image stacks which was produced as
part of the Cluster Difference Imaging Photometric Survey (CDIPS;
\citealt{bouma_cluster_2019}).  Our CDIPS lightcurve of choice used a
circular aperture with radius 1 pixel.

@@

\tn\ has been reported as a member of \cn\ by multiple independent 
investigators \citep{Kharchenko_et_al_2013,cantatgaudin_gaia_2018}.
%FIXME FIXME finish these citations

@@

@@

\tn\ is in its expected position relative to the other members along
the cluster isochrone.  This photometrically limits the presence of
binary companions in the \tn\ system, to a magnitude difference of
perhaps half the brightness of the target star.

Figure~\ref{fig:hr} also suggests that the membership census of \cn\
is incomplete.  We defined the reference ``neighborhood'' as the group
of at most $10^4$ randomly selected non-member stars within 5 standard
deviations of the mean \cn\ right ascension, declination, and
parallax.  We queried Gaia DR2 for these stars using
\texttt{astroquery} \citep{astroquery_2018}.  Many low-mass stars
appear above the main sequence, even though they were not identified
as 5-dimensional kinematic members through the unsupervised
\citet{cantat-gaudin_gaia_2018} membership assignment process.

\subsubsection{Position and Kinematics}

\begin{figure*}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ 
  {\bf Positions and kinematics of \tn\ (star), \cn\ members (black),
  and stars in the neighborhood (gray).} Members (black circles) were
  identified by \citet{cantatgaudin_gaia_2018}.  $\alpha$ denotes
  right ascension, $\delta$ declination, $\pi$ parallax, $\mu_{\rm
  delta}$ and $\mu_{\rm \alpha}$ proper motion in each equatorial
  direction, and ${\rm RV}$ radial velocity reported by Gaia-DR2.  The
  RVs are for unblended spectra of bright stars ($G\lesssim 12$).  The
  proper motion projection ($\mu_{\rm delta}$ vs{.} $\mu_{\rm
  \alpha}\cos\delta$) highlights the incomplete membership selection
  function.
  \label{fig:full_kinematics}
	}
\end{figure*}

We examine the six-dimensional positions and kinematics in greater
depth in Figure~\ref{fig:full_kinematics}.  The ``neighborhood'' is
defined here identically to as in Figure~\ref{fig:hr}.  The axes
limits for the right ascension, declination, and parallax dimensions
are as in the Gaia archive query.  The axes limits for the proper
motion and radial velocity dimensions are set at the 25$^{\rm th}$ and
75$^{\rm th}$ percentiles, in order to give a sense of the
population's distribution, while excluding outlying points.  The
radial velocities suffer the greatest incompleteness due to the
current $G\approx12$ magnitude limit of the Gaia-DR2 data processing.

Figure~\ref{fig:full_kinematics} provides strong evidence {\it (i)} for the
existence of the \cn\ open cluster and {\it (ii)} for the membership
of \tn\ within \cn.
The only dimension that could perhaps lead to some worry is the
parallax, as \tn\ is one of the closest \cn\ members reported by
\citet{cantatgaudin_gaia_2018}.
Fortunately, there are independent means of verifying stellar youth.

@@

% \appendix
% \section{Gaia query}
% bounding by 5 stdevns
% Launched query: '
%         select top 10000
%             g.source_id, g.phot_bp_mean_mag, g.phot_rp_mean_mag,
%             g.phot_g_mean_mag, g.parallax, g.ra, g.dec, g.pmra, g.pmdec,
%             g.radial_velocity, g.radial_velocity_error
%         from gaiadr2.gaia_source as g
%         where
%             g.parallax > 5.69
%         and
%             g.parallax < 7.41
%         and
%             g.dec < -58.41
%         and
%             g.dec > -70.33
%         and
%             g.ra > 145.01
%         and
%             g.ra < 175.85
%         and
%             g.phot_g_mean_mag < 18
%         order by
%             random_index
